\section{Results}
\subsection*{Confirmatory Factor Analysis}
Preliminary Discussion:

- In the base article \cite{furlanComplementarityLeanManufacturing2011}, they have only six practices for each bundle.

- Should we create subsamples to get down to six per factor, or is it okay to include everything?

- The majority of loadings are above 0.8, and all statistically significant (p < 0.01).

- We tried bundling sustainability outcomes at some stage too, but in the end, it seemed irrelevant to our research questions.

- We also conducted an EFA to see if we could further breakdown the bundles (specifically environmental practices, which is a massive group).

- We did not include EFA results here as it did not seem relevant to the research questions (should we include it or better use this time to diagnose our other models).

\input{tables/cfa}
\subsection*{Practice Adoption}
Preliminary Discussion:

- Staying with \cite{furlanComplementarityLeanManufacturing2011}, we have created dummy variables for the study as seen in Table 2.

- We will need to discuss how these dummy variables were created (splitting at the median point for high/low and then expanding to 4 categories based on the binary combinations).

- We still have not run a t-test to confirm statistically significant means between dummy variables as per \cite{furlanComplementarityLeanManufacturing2011}.

\input{tables/performance_means}
\subsection*{Tukey Analysis}
Preliminary Discussion:

- The Tukey analysis shows that the means of environmental performance differences are not statistically significant in certain cases.

- This fact seems to already reject H0 as we have no difference in performance between the combination and the singular (mainly environmental).

- For this reason, we probably do not need to run the OLS regression for complementarity as we can already see the marginal performance difference is not present.

- What can we do to validate the assumptions of this modeling?

\input{tables/tukey_results}
\subsection*{Regression Models}
Preliminary Discussion:

- For our regression models, we have taken means of our CFA bundles (JIT and Env) and used them as the independent variables.

- Again, we need to understand what the most important assumptions for this model are and how to validate them.

- So far (controlling for plant size), we see no statistically significant results for the regression models besides environmental practices as correlated to emissions to air.

- These results are surprising and make us question the validity of our models.

- Is the reason for these results the fact that we bundle over 40 practices, and the dependent variables are too singular?

- How can we diagnose and improve our models?

- General comment for all models: we have not checked the 6 assumptions of linear models.

- Where is most imporant to check for: normality, homoscedasticity, multicollinearity, autocorrelation, and linearity?

\input{tables/regression_air_table}
\input{tables/regression_waste_table}
